Competing Bandits: The Perils of Exploration under Competition

### 2018-09-05 paper/content/inverted_u.tex
Added a para re why EoG values increase with T0.

\begin{finding}
\textit{
Under permanent duopoly, \Eeog values tend to be much smaller than the time horizon $T$, but tend to increase as the warm start $T_0$ increases.
}
\end{finding}

\ascomment{Can we cook up an explanation for why \Eeog grows with $T_0$?}

>>>>

\begin{finding}
\textit{
Under permanent duopoly, \Eeog values tend to be much smaller than the time horizon $T$. 
}
\end{finding}

\asedit{We also see that the \Eeog values tend to increase as the warm start $T_0$ increases. We conjecture this is because larger $T_0$ tends to help a better algorithm. Indeed, we know that the ``effective end of game" in this scenario typically occurs when a better algorithm loses, and helping it delays the loss.}
